Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

We argue that $(r_1,...,r_{k-3}, r_{k-2},h,v)$ belongs to $\J_2$. Let $p$ be the intersection point of $h'$ and $v$. As $h'$ is contained in $h$, the intersection point between $h$ and $v$ is also $p$. Since $(r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$, it must hold that $p$ falls in $r_i$ for $i \in [k-3]$. From our earlier discussion, we already know that $r_{k-2}$ contains $h'$; hence, $p$ falls in $r_{k-2}$ as well. Thus, $h \cap v \cap \bigcap_{i = 1}^{k-2}r_i$ is non-empty, indicating that $(r_1,...,r_{k-3}, r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$. This, together with the fact that $r_{k-2}$ covers the left endpoint of $h$, tells us $(r_1,...,r_{k-3}, r_{k-2},h,v) \in \J_2$.

>>>>

We argue that $(r_1,...,r_{k-3}, r_{k-2},h,v)$ belongs to $\J_2$. Let $p$ be $h' \cap v$ (the intersection point of $h'$ and $v$). As $h'$ is contained in $h$, it must hold that $h \cap v = p$. Since $(r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$, we know that $p$ falls in all of $r_1, ..., r_{k-3}$. Our earlier discussion already shows that $r_{k-2}$ contains $h'$; this means that $p$ falls in $r_{k-2}$. Thus, $h \cap v \cap \bigcap_{i = 1}^{k-2}r_i$ cannot be empty as it equals $p$. We can now conclude that $(r_1,...,r_{k-3}, r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$. This, together with the fact that $r_{k-2}$ covers the left endpoint of $h$, tells us $(r_1,...,r_{k-3}, r_{k-2},h,v) \in \J_2$.
